---
title: "R Series Episode 2: <br/>"
subtitle: "Creating Awsome Web Slides in Quarto with revealjs"
author: "Dr. Kam Tin Seong"
institute: "School of Computing and Information Systems, SMU"
date: "`r Sys.Date()`"
format: 
  revealjs:
    theme: sky
    width: 1600
    height: 900
    incremental: false
execute: 
  eval: true
  echo: true
  warning: false
editor: visual
---

## Why you are here?

::: incremental
Because you are:

-   tired of creating PowerPoint slides.
-   interested to create awesome web slides using R.
:::

## Getting Started

Code chunk below perform the following tasks:

-   loading **knitr**, **DT**, and **tidyverse** family of r packages onto R environment by using `p_load()` of **pacman** package.
-   importing *Exam_data.csv* into R and save it as a tibble data frame by using `read_csv()` of **readr** package.

```{r}
pacman::p_load(tidyverse, knitr, DT)

exam_data <- read_csv("data/Exam_data.csv")
```

## Hello Plot

The histogram reveals the distribution of Maths scores.

```{r}
#| echo: false
#| fig-width: 8
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```

::: callout-tip
Refer to the quarto file for the code chunk used.
:::

------------------------------------------------------------------------

### Dual columns slide

This slide uses `columns` function of Quarto to create a split the display area into two equal parts.

::: callout-tip
Refer to the quarto file for the code chunk used.
:::

:::::: columns
:::: {.column width="50%"}
The code chunk.

::: {style="font-size: 1.20em"}
```{r}
#| eval: false
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
:::
::::

::: {.column width="50%"}
The plot

```{r}
#| echo: false
#| fig-height: 6
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
:::
::::::

------------------------------------------------------------------------

### Working with Tabsets

This slide uses `panel-tabset` function of Quarto to create two tabset panels. One for displaying the code chunk used to plot the histogram and the other one, for displaying the histogram.

:::: panel-tabset
## The code chunk

::: {style="font-size: 1.35em"}
```{r}
#| eval: false
#| code-line-numbers: "7"
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
:::

## The plot

```{r}
#| echo: false
#| fig-height: 6
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
::::

::: callout-tip
Refer to the quarto file for the code chunk used.
:::

## Adding Table

### Static html table

This slide shows an example of displaying a professional looking table on Quarto using `kable()` of **knitr** package.

```{r}
#| echo: false
head(exam_data) %>%
  knitr::kable(format = "html")
```

::: callout-tip
Refer to the quarto file for the code chunk used.
:::

------------------------------------------------------------------------

### Interactive table

This slide shows an example of displaying a professional looking table on Quarto using `datatable()` of **DT** package.

```{r}
#| echo: false
datatable(data = exam_data, 
  options = list(
    scrollY = "400px",
    scrollX = TRUE,
    scrollCollapse = TRUE,
    paging = FALSE),
    width = "100%")
```

::: callout-tip
Refer to the quarto file for the code chunk used.
:::
