---
title: "My First Date with Quarto"
author: "Dr. Kam Tin Seong"
date: "September 15, 2025"
date-modified: "last-modified"
format:
  html:
    theme: default
    toc: true
    number-sections: true
execute: 
  eval: true
  echo: true
  warning: false
  freeze: true
editor: visual
---

## Getting Started

Code chunk below perform the following tasks:

-   loading **knitr**, **DT**, and **tidyverse** family of r packages onto R environment by using `p_load()` of **pacman** package.
-   importing *Exam_data.csv* into R and save it as a tibble data frame by using `read_csv()` of **readr** package.

```{r}
pacman::p_load(tidyverse, knitr, DT)

exam_data <- read_csv("data/Exam_data.csv")
```

## Hello Plot

Code chunk below is used to plot a histogram of Maths score by using functions of **ggplot2** package.

::: {style="font-size: 1.20em"}
```{r}
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "pink") +
  ggtitle("Distribution of Maths Scores")
```
:::

### Dual columns slide

In this sub-sections, `columns` function of Quarto is used to split the display area into two equal parts.

:::::: columns
:::: {.column width="50%"}
The code chunk.

::: {style="font-size: 1.00em"}
```{r}
#| eval: false
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
:::
::::

::: {.column width="50%"}
The plot

```{r}
#| echo: false
#| fig-height: 6
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
:::
::::::

### Working with tableset panel

In this sub-section, `panel-tabset` function of Quarto is used to create two tabset panels. One for displaying the code chunk used to plot the histogram and the other one, for displaying the histogram.

:::: panel-tabset
## The code chunk

::: {style="font-size: 1.35em"}
```{r}
#| eval: false
#| code-line-numbers: "7"
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
:::

## The plot

```{r}
#| echo: false
#| fig-height: 6
ggplot(data = exam_data,
        aes(x = MATHS)) +
  geom_histogram(bins = 10,
                 boundary = 100,
                 color = "black",
                 fill = "light blue") +
  ggtitle("Distribution of Maths Scores")
```
::::

## Adding Table

### Static html table

This slide shows an example of displaying a professional looking table on Quarto using `kable()` of **knitr** package.

```{r}
#| echo: false
head(exam_data) %>%
  knitr::kable(format = "html")
```

### Interactive table

This slide shows an example of displaying a professional looking table on Quarto using `datatable()` of **DT** package.

```{r}
#| echo: false
datatable(data = exam_data, 
  options = list(
    scrollY = "400px",
    scrollX = TRUE,
    scrollCollapse = TRUE,
    paging = FALSE),
    width = "100%")
```
